Probing the Deuteron at Very Large Internal Momenta

### 2020-06-30 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/body.tex
updated

\includegraphics[scale=0.46]{prl_plots/PRL_plot1_WJC2.pdf}

@@

cross sections using the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} NN potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.
For the WJC2 (orange) potential, the calculations were done by Orden and Jeschonnek \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states. The calculations
used two different form factor parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a discrepancy of $\sim5.8-6.6 \%$ was found between the respective
WJC2 reduced cross sections. Figure \ref{fig:fig1} shows the results using only the WJC2 (GKex05) parametrization. \\
\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris,
AV18 and WJC2 models increasingly differ from the CD-Bonn calculation. In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c whereas
the WJC2 PWIA falls off with a comparatively smaller cross section at $\theta_{nq}=35^{\circ}$. The CD-Bonn cross sections in contrast are generally smaller than the Paris, AV18 and WJC2 in this region.
\indent Moreover, in spite of the partial agreement between data and theory, between $p_{\mathrm{r}} \sim 0.55$ and 1.0 GeV/c, all models exhibit a
4.241 standard deviations was found between the data and theory slopes which corresponds to a probability $\leq 1.1\times 10^{-5}$ (very unlikely) that the observed discrepancy is due to a statistical fluctuation. \\ 

@@

this potential. Paris and AV18 potentials are phenomenological in which the 

@@

same NN scattering phase-shifts. The major difference between CD-Bonn and Paris/AV18 
potentials is that the former predicts much softer repulsive interaction at short distance which 

@@

%The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant
%(original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18
%groups to describe the NN potential.

@@

@@

\indent For $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig2]{2(a),(b)}), the data are best described by the CD-Bonn PWIA calculation for recoil momenta up

@@

missing momenta typically above 800 MeV/c for the CD-Bonn

@@

\includegraphics[scale=0.5]{./prl_plots/PRL_plot2_WJC2.pdf}

@@

The dashed reference (magenta) line refers to CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}

@@

At $\theta_{nq}=45^{\circ}$, the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\

@@

Furthermore, the CD-Bonn model was found to be significantly different than the Paris, AV18 or WJC2 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.

>>>>

\includegraphics[scale=0.46]{prl_plots/PRL_plot1.pdf}

@@

cross sections using wave functions determined from the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} NN potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA, referred to as MS, and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach, referred to as JML.
For the WJC2 (orange) potential, the calculations were carried out by Jeschonnek and Van Orden \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states, which will be labeled JVO. The calculations
used two different form factor parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a difference of $\sim5.8-6.6 \%$ was found between the respective
JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\

@@

this potential. Paris and AV18 are purely phenomenological potentials where a 

@@

same NN scattering phase-shifts. The major difference between the CD-Bonn and Paris/AV18 
potentials is that the former predicts a much softer repulsive interaction at short distance which 

@@

@@

\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the JML,
MS AV18 and JVO models increasingly differ from the MS CD-Bonn calculation. In this region, the JML and MS AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c whereas
the JVO PWIA falls off with a comparatively smaller cross section at $\theta_{nq}=35^{\circ}$. The MS CD-Bonn cross sections in contrast are generally smaller than the JML, MS AV18 and JVO in this region.
\indent Between data and theory, for recoil momenta $p_{\mathrm{r}} \sim 0.55-1.0$ GeV/c, all models exhibit a
4.2 standard deviations was found between the data and theory slopes which corresponds to a probability $\leq 1.1\times 10^{-5}$ (very unlikely) that the observed discrepancy is due to a statistical fluctuation. \\ 

@@

\indent For $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig2]{2(a),(b)}), the data are best described by the MS CD-Bonn PWIA calculation for recoil momenta up

@@

missing momenta typically above 800 MeV/c for the MS CD-Bonn

@@

\includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}

@@

The dashed reference (magenta) line refers to MS CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}

@@

At $\theta_{nq}=45^{\circ}$, the FSI dominance starts earlier for all models above 800 MeV/c and for the MS CD-Bonn based calculation above 600 MeV/c. \\

@@

Furthermore, the MS CD-Bonn model was found to be significantly different than the JML, MS AV18 or JVO models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.

### 2020-06-30 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/intro-rev.tex
updated

nucleons begin to overlap. The dynamics in this short distance region is directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Barack_2019,RevModPhys.89.045002}.

@@

having to include explicit quark degrees of freedoms, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}. As of the present time, there are only a few nuclear physics experiments for

@@

to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{\mathrm{r}}\sim 1$ GeV/c, which is almost double of the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.

>>>>

nucleons begin to overlap. The dynamics in this short distance region are directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Barack_2019,RevModPhys.89.045002}.

@@

having to include explicit quark degrees of freedom, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}. As of the present time, there are only a few nuclear physics experiments for

@@

to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{\mathrm{r}}\sim 1$ GeV/c, which is almost double the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.

### 2020-06-30 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/body.tex
updated

$p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$. For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$ . The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square). The good agreement between the Hall A and C data at lower $p_{\mathrm{r}}$

@@

The data are compared to theoretical reduced
cross sections using the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38} and Paris \cite{PhysRevC.21.861} NN-potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.\\

@@

\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
AV18 models increasingly differ from the CD-Bonn calculation. In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c. The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.  In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c (Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).\\
\indent The difference between the deuteron wave functions with CD-Bonn and Paris/AV18 potentials is 
The CD-Bonn model is based on the One-Boson-Exchange approach in which the 
this potential. Paris and AV18 potentials are phenomenological in which the 
same NN scattering phase-shifts. The major difference between CD-Bonn and Paris/AV18 
potentials is that the former predicts much softer repulsive interaction at short distance which 
%The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant
%(original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18
%groups to describe the NN potential.
The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\

@@

At $\theta_{nq}=45^{\circ}$, the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\
\indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_{\mathrm{r}}$ dependence above 600 MeV/c in a region where FSI are still relatively small $(<30\%)$.  This behavior of the data is new
and additional data in this kinematic region are necessary to improve the statistics. \\

@@

Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.

@@

thank Misak Sargsian, Sabine Jeschonnek and J.W.Van Orden for providing the theoretical calculations as well as the useful

>>>>

$p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$. For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$. The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square). The good agreement between the Hall A and C data at lower $p_{\mathrm{r}}$

@@

The data are compared to theoretical calculations using wave functions determined from the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} NN potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA, referred to as MS, and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach, referred to as JML.
For the WJC2 (orange) potential, the calculations were carried out by Ford, Jeschonnek and Van Orden \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states, which will be labeled JVO. The calculations
used two different form factor parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a difference of $\sim5.8-6.6 \%$ was found between the respective
JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\
\indent The difference between the deuteron wave functions with CD-Bonn, Paris, AV18 and WJC2 potentials is 
The CD-Bonn model is based on the One-Boson-Exchange Potential (OBEP) approach in which the 
this potential. In contrast, the WJC2 is a OBEP derived within the Covariant Spectator Theory (CST) \cite{PhysRev.186.1448, PhysRevD.10.223, PhysRevC.26.2203, PhysRevC.26.2226}
which require comparatively few parameters while still producing a high-precision fit to the NN scattering data.
The Paris and AV18 are purely phenomenological potentials where a 
same NN scattering phase-shifts. The major difference between the CD-Bonn and Paris/AV18/WJC2 
potentials is that the former predicts a much softer repulsive interaction at short distance which 
The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}.\\

@@

\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the JML,
MS AV18 and JVO models increasingly differ from the MS CD-Bonn calculation. In this region, the JML and MS AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c whereas
the JVO PWIA falls off with a comparatively smaller cross section at $\theta_{nq}=35^{\circ}$. The MS CD-Bonn cross sections in contrast are generally smaller than the JML, MS AV18 and JVO in this region.
In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c
(Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).\\
\indent Between data and theory, for recoil momenta $p_{\mathrm{r}} \sim 0.55-1.0$ GeV/c, all models exhibit a
steeper fall-off compared to data. This discrepancy was quantified by doing a linear fit to the data and each of the PWIA calculations. A difference of at least
4.2 standard deviations was found between the data and theory slopes which corresponds to a probability $\leq 1.1\times 10^{-5}$ (very unlikely) that the observed discrepancy is due to a statistical fluctuation. \\ 

@@

At $\theta_{nq}=45^{\circ}$, the FSI dominance starts earlier for all models above 800 MeV/c and for the MS CD-Bonn based calculation above 600 MeV/c. \\
\indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_{\mathrm{r}}$ dependence above 600 MeV/c in a
region where FSI are still relatively small $(<30\%)$. This behavior of the data is new and additional data in this kinematic region are necessary
to improve the statistics. \\

@@

Furthermore, the MS CD-Bonn model was found to be significantly different than the JML, MS AV18 or JVO models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.

@@

thank Misak Sargsian, J.M. Laget, Sabine Jeschonnek and J.W. van Orden for providing the theoretical calculations as well as the useful
